\section{Leadership Transfer} \label{sec:leadership}

In some cases, one or more servers may be more suitable to lead the cluster than others. For 
example, a server with high load would not make a good leader, or in a WAN deplolyment, 
servers in a primary datacenter may be preferred in order to optimize the latency between clients 
and the leader. Since \smrsystem needs a server with a sufficiently up-to-date log to become leader, 
which might not be the most preferred one. Instead, a leader in \xxx can periodically check 
to see whether one of its available followers would be more suitable, and if so, transfer its 
leadership to that server.
To transfer leadership in \xxx, the prior leader sends its log entries to the target server, then 
the target server runs an election without waiting for an election timeout to elapse. The following 
steps describe the process in more detail:

\begin{enumerate}
\item The prior leader stops accepting new client requests.
\item The prior leader fully updates the target server's log to match its own, using the normal log 
replication mechanism in \smrsystem.
\item The prior leader sends a \timeoutnow request to the target server. This request has the same effect as 
the target server's election time firing: the target server starts a new election.
\end{enumerate}

Once the target server receives the \timeoutnow request, it is highly likely to start an election before 
any other server and become leader. At this point, leadership transfer is complete.

